### 2020-06-15 README.Rmd
The HURDAT2 wind radii are to observations during a specific storm than the modeled data.
I added question marks on either side of this sentence because it doesn't seem like it is complete but I'm not sure what it is supposed to read as.
more closely aligned in readme
removing a colon
removing a colon in one of the FIPS examples for consistency with the others

The HURDAT2 wind radii are to observations during a specific storm than the modeled data. In certain cases, especially storms in extratropical transition, this dataset might be preferable to the modeled wind speeds, even though it provides less continuous estimates. This source of wind data can be specified using the `wind_source` option in the `county_wind` function. For example, to generate a list of all storms in Orleans Parish with maximum sustained winds of 34 knots or more based on the HURDAT2 wind radii, you can run:

@@

Finally, you can use the `county_events` function to get a listing of all storms for which a county had a certain type of NOAA Storm Events listing. For example, to get a list of all storms for which Norfolk, Virginia, (FIPS: 51710) had a flood event listing, you can run:

>>>>

The HURDAT2 wind radii are more closely aligned to observations during a specific storm than the modeled data. In certain cases, especially storms in extratropical transition, this dataset might be preferable to the modeled wind speeds, even though it provides less continuous estimates. This source of wind data can be specified using the `wind_source` option in the `county_wind` function. For example, to generate a list of all storms in Orleans Parish with maximum sustained winds of 34 knots or more based on the HURDAT2 wind radii, you can run:

@@

Finally, you can use the `county_events` function to get a listing of all storms for which a county had a certain type of NOAA Storm Events listing. For example, to get a list of all storms for which Norfolk, Virginia, (FIPS 51710) had a flood event listing, you can run:
